\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{float}

\begin{document}

\noindent
\textbf{March 6, 2026} \hfill \textbf{Joseph DeLeonardis} \\
\textbf{UIN: 0820000866} \\
\textbf{CSCE-636-700} \\
\textbf{Deep Learning Homework \#5}

\section*{Problem 1}

\subsection*{Chapter 10: Interpreting what ConvNets learn}
This chapter built upon the model created in Chapter 8 using the dogs and cats dataset. Running the Chapter 10 coding exercises demonstrated three key concepts in ConvNet interpretability: layers, gradients, and heatmaps. As a network goes deeper, learned features become increasingly abstract early layers capture basic edges and textures while deeper layers respond to complex concepts like facial features. Grad-CAM heatmaps tie this together by revealing which regions of an image most influenced the model's prediction, providing a visual sanity check that the model is making decisions for the right reasons.
\newline
The visualizations for sections 1 through 3 are included in the compiled .ipynb file located in the chapter\_10 folder.

\subsection*{Chapter 11: Image Segmentation}
Chapter 11 covers the three types of image segmentation and the distinctions between them. To satisfy the requirements of problem 1 part 4, I modified the image selection after loading the oxford\_segmentation model by replacing the hardcoded index with a randomly generated one, ensuring the segmentation results are drawn from a random sample rather than a fixed image.


\section*{Problem 2}


\subsection*{Chapter 13: Timeseries forecasting}

The original code was modified to predict temperature 48 hours ahead instead of 24 hours by changing the delay parameter. This resulted in a slightly higher MAE across all 6 methods, which is expected predicting further into the future introduces more uncertainty. Both notebooks are attached under the chapter\_13 folder for reference.

\begin{table}[H]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Method} & \textbf{24hr Test MAE} & \textbf{48hr Test MAE} \\
\midrule
Try 1 -- Common-sense Baseline       & 2.62 & 3.47 \\
Try 2 -- Dense Neural Network        & 2.64 & 3.21 \\
Try 3 -- 1D Convolutional Network    & 3.09 & 3.85 \\
Try 4 -- LSTM with Recurrent Dropout & 2.16 & 2.91 \\
Try 5 -- Stacked RNN                 & 2.44 & 3.19 \\
Try 6 -- Bidirectional RNN           & 2.07 & 2.53 \\
\bottomrule
\end{tabular}
\caption{Test MAE comparison for 24-hour vs.\ 48-hour temperature prediction across all 6 methods.}
\end{table}



\end{document}
